Supporting Information : Asymmetric tail-dependence in extreme climatic events affects population-extinction risk

### 2019-08-29 SuppMat.Rmd
started editing results

pdf("./Results/common_legend.pdf",height=1,width=12)
op<-par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 0, 0, 0))
plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
legend("center", c("noise : LTdep.","noise : RTdep."), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'),x.intersp = 0.2,
         cex = 2.5, xpd = TRUE, horiz = T, inset = c(0,0), 
         bty = "n")
par(op)
dev.off()

@@

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
legend(x=0.7,y=1.05, c("noise : LTdep.","noise : RTdep."), lty=c(1,1), pch=c(1,1), 
       col=c('red', 'blue'), horiz=F, bty='o', cex=1.5, adj=0)
mtext(paste("Ricker model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
#mtext(paste("(K = 50, sd = 1)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
mtext(expression( paste("( K = 50, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
getplot(x=x,rlist = rlist,noisetype = "extreme")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Hassell model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.5, b = 100, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_hassell_local
rlist<-hassell_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "extreme")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Maynard Smith model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.5, b = 4, ", sigma,"=0.8 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_msmith_local
rlist<-msmith_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "extreme")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Pennycuick model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.1, b = 0.1, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_pennycuick_local
rlist<-pennycuick_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "extreme")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Verhulst model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( K = 1, ", sigma,"=0.6 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_verhulst_local
rlist<-verhulst_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "extreme")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Austin-Brewer model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( s = 0.2, K = 50, ", sigma,"=0.6 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_abrewer_local
rlist<-abrewer_extrisk_d0$r
getplot(x=x,rlist = rlist,noisetype = "extreme")

@@

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
legend(x=0.7,y=1.05, c("noise : LTdep.","noise : RTdep."), lty=c(1,1), pch=c(1,1), 
       col=c('red', 'blue'), horiz=F, bty='o', cex=1.5, adj=0)
mtext(paste("Ricker model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
#mtext(paste("(K = 50, sd = 1)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
mtext(expression( paste("( K = 50, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
getplot(x=x,rlist = rlist,noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Hassell model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.5, b = 100, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_hassell_local
rlist<-hassell_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Maynard Smith model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.5, b = 4, ", sigma,"=0.8 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_msmith_local
rlist<-msmith_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Pennycuick model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.1, b = 0.1, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_pennycuick_local
rlist<-pennycuick_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Verhulst model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( K = 1, ", sigma,"=0.6 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_verhulst_local
rlist<-verhulst_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Austin-Brewer model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( s = 0.2, K = 50, ", sigma,"=0.6 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_abrewer_local
rlist<-abrewer_extrisk_d0$r
getplot(x=x,rlist = rlist,noisetype = "moderate")

@@

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
legend(x=0.7,y=1.05, c("noise : LTdep.","noise : RTdep."), lty=c(1,1), pch=c(1,1), 
       col=c('red', 'blue'), horiz=F, bty='o', cex=1.5, adj=0)
mtext(paste("Ricker model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( K = 50, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
getplot(x=x,rlist = rlist, noisetype = "extreme")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Hassell model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.5, b = 100, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_hassell_global
rlist<-hassell_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "extreme")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Maynard Smith model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.5, b = 4, ", sigma,"=0.8 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_msmith_global
rlist<-msmith_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "extreme")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Pennycuick model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.1, b = 0.1, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_pennycuick_global
rlist<-pennycuick_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "extreme")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Verhulst model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( K = 1, ", sigma,"=0.6 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_verhulst_global
rlist<-verhulst_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "extreme")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Austin-Brewer model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( s = 0.2, K = 50, ", sigma,"=0.6 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_abrewer_global
rlist<-abrewer_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "extreme")

@@

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
legend(x=0.7,y=1.05, c("noise : LTdep.","noise : RTdep."), lty=c(1,1), pch=c(1,1), 
       col=c('red', 'blue'), horiz=F, bty='o', cex=1.5, adj=0)
mtext(paste("Ricker model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( K = 50, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
getplot(x=x,rlist = rlist, noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Hassell model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.5, b = 100, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_hassell_global
rlist<-hassell_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Maynard Smith model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.5, b = 4, ", sigma,"=0.8 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_msmith_global
rlist<-msmith_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Pennycuick model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.1, b = 0.1, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_pennycuick_global
rlist<-pennycuick_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Verhulst model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( K = 1, ", sigma,"=0.6 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_verhulst_global
rlist<-verhulst_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Austin-Brewer model : "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( s = 0.2, K = 50, ", sigma,"=0.6 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_abrewer_global
rlist<-abrewer_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "moderate")

@@

<!--Supp. FIG : Ricker model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Ricker metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Ricker dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_ricker_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Hassell model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/hassell_scl_1/hassell_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Hassell metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Hassell dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_hassell_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Maynard smith model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Maynard smith metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Maynard Smith dynamics with local dispersal; 
numsims=10000, $\sigma$=0.8. \label{fig_msmith_risk_local_disp_scl_0.8}}
\end{center}
\end{figure}

<!--Supp. FIG : Pennycuick model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Pennycuick metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Pennycuick dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_risk_local_disp_pennycuick_r_vary_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Verhulst model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Verhulst metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Verhulst dynamics with local dispersal; 
numsims=10000, $\sigma$=0.6. \label{fig_risk_local_disp_verhulst_r_vary_scl_0.6}}
\end{center}
\end{figure}

>>>>

pdf("./Results/common_legend_extreme_noise.pdf",height=1,width=12)
op<-par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 0, 0, 0))
plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
legend("center", c("noise: extreme LTdep.","noise: extreme RTdep."), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'),x.intersp = 0.2,
         cex = 2.5, xpd = TRUE, horiz = T, inset = c(0,0), 
         bty = "n")
par(op)
dev.off()

pdf("./Results/common_legend_moderate_noise.pdf",height=1,width=12)
op<-par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 0, 0, 0))
plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
legend("center", c("noise: moderate LTdep.","noise: moderate RTdep."), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'),x.intersp = 0.2,
         cex = 2.5, xpd = TRUE, horiz = T, inset = c(0,0), 
         bty = "n")
par(op)
dev.off()

@@

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
legend("topleft", c("noise: extreme LTdep.","noise: extreme RTdep."), lty=c(1,1), pch=c(1,1), 
       col=c('red', 'blue'), horiz=F, bty='o', cex=1.5, adj=0, x.intersp=0.2)
mtext(paste("Ricker model: "), side = 3, line=-7, adj=0.3, cex=1, col="black")
#mtext(paste("(K = 50, sd = 1)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
mtext(expression( paste("( K = 50, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
getplot(x=x,rlist = rlist,noisetype = "extreme")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Hassell model: "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.5, b = 100, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_hassell_local
rlist<-hassell_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "extreme")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Maynard Smith model: "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.5, b = 4, ", sigma,"=0.8 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_msmith_local
rlist<-msmith_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "extreme")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Pennycuick model: "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.1, b = 0.1, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_pennycuick_local
rlist<-pennycuick_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "extreme")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Verhulst model: "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( K = 1, ", sigma,"=0.6 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_verhulst_local
rlist<-verhulst_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "extreme")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Austin-Brewer model: "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( s = 0.2, K = 50, ", sigma,"=0.6 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_abrewer_local
rlist<-abrewer_extrisk_d0$r
getplot(x=x,rlist = rlist,noisetype = "extreme")

@@

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
legend("topleft", c("noise: moderate LTdep.","noise: moderate RTdep."), lty=c(1,1), pch=c(1,1), 
       col=c('red', 'blue'), horiz=F, bty='o', cex=1.5, adj=0, x.intersp=0.2)
mtext(paste("Ricker model: "), side = 3, line=-7, adj=0.3, cex=1, col="black")
#mtext(paste("(K = 50, sd = 1)"), side = 3, line=-8.2, adj=0.6, cex=1, col="black")
mtext(expression( paste("( K = 50, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
getplot(x=x,rlist = rlist,noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Hassell model: "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.5, b = 100, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_hassell_local
rlist<-hassell_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Maynard Smith model: "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.5, b = 4, ", sigma,"=0.8 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_msmith_local
rlist<-msmith_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Pennycuick model: "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.1, b = 0.1, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_pennycuick_local
rlist<-pennycuick_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Verhulst model: "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( K = 1, ", sigma,"=0.6 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_verhulst_local
rlist<-verhulst_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Austin-Brewer model: "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( s = 0.2, K = 50, ", sigma,"=0.6 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_abrewer_local
rlist<-abrewer_extrisk_d0$r
getplot(x=x,rlist = rlist,noisetype = "moderate")

@@

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
legend("topleft", c("noise: extreme LTdep.","noise: extreme RTdep."), lty=c(1,1), pch=c(1,1), 
       col=c('red', 'blue'), horiz=F, bty='o', cex=1.5, adj=0,x.intersp=0.2)
mtext(paste("Ricker model: "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( K = 50, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
getplot(x=x,rlist = rlist, noisetype = "extreme")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Hassell model: "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.5, b = 100, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_hassell_global
rlist<-hassell_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "extreme")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Maynard Smith model: "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.5, b = 4, ", sigma,"=0.8 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_msmith_global
rlist<-msmith_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "extreme")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Pennycuick model: "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.1, b = 0.1, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_pennycuick_global
rlist<-pennycuick_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "extreme")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Verhulst model: "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( K = 1, ", sigma,"=0.6 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_verhulst_global
rlist<-verhulst_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "extreme")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Austin-Brewer model: "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( s = 0.2, K = 50, ", sigma,"=0.6 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_abrewer_global
rlist<-abrewer_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "extreme")

@@

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
legend("topleft", c("noise: moderate LTdep.","noise: moderate RTdep."), lty=c(1,1), pch=c(1,1), 
       col=c('red', 'blue'), horiz=F, bty='o', cex=1.5, adj=0, x.intersp=0.2)
mtext(paste("Ricker model: "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( K = 50, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
getplot(x=x,rlist = rlist, noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Hassell model: "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.5, b = 100, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_hassell_global
rlist<-hassell_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Maynard Smith model: "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.5, b = 4, ", sigma,"=0.8 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_msmith_global
rlist<-msmith_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Pennycuick model: "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( a = 0.1, b = 0.1, ", sigma,"=1 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_pennycuick_global
rlist<-pennycuick_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Verhulst model: "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( K = 1, ", sigma,"=0.6 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_verhulst_global
rlist<-verhulst_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "moderate")

plot(1, 0, bty = "n", xaxt = "n", yaxt = "n",xlab="",ylab="",type="n")
mtext(paste("Austin-Brewer model: "), side = 3, line=-7, adj=0.3, cex=1, col="black")
mtext(expression( paste("( s = 0.2, K = 50, ", sigma,"=0.6 )" )),side = 3, line=-9, adj=0.6, cex=1, col="black")
x<-res_abrewer_global
rlist<-abrewer_extrisk_d0$r
getplot(x=x,rlist = rlist, noisetype = "moderate")

@@

<!--Supp. FIG : Ricker model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Ricker metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Ricker dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_ricker_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Hassell model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/hassell_scl_1/hassell_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Hassell metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Hassell dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_hassell_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Maynard smith model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Maynard smith metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Maynard Smith dynamics with local dispersal; 
numsims=10000, $\sigma$=0.8. \label{fig_msmith_risk_local_disp_scl_0.8}}
\end{center}
\end{figure}

<!--Supp. FIG : Pennycuick model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Pennycuick metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Pennycuick dynamics with local dispersal; 
numsims=10000, $\sigma$=1. \label{fig_risk_local_disp_pennycuick_r_vary_scl_1}}
\end{center}
\end{figure}

<!--Supp. FIG : Verhulst model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Verhulst metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Verhulst dynamics with local dispersal; 
numsims=10000, $\sigma$=0.6. \label{fig_risk_local_disp_verhulst_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--Supp. FIG : Austin-Brewer model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=10 cm]{./Results/common_legend_extreme_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/austinbrewer_scl_0.6/abrewer_ext_risk_local_disp_extremenoise.pdf}\\
\caption[Effect of extreme tail-dependent environmental noises on extinction risk for Austin-Brewer metapopulation model with local dispersal.]{Effect of extreme tail-dependent environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Austin-Brewer dynamics with local dispersal; 
numsims=10000, $\sigma$=0.6. \label{fig_risk_local_disp_abrewer_r_vary_scl_0.6}}
\end{center}
\end{figure}
